---
title: "NBA Height analysis"
output: github_document
---
## Purpose

Today my flatmate and I were watching the NBA and saw a huge dunk. I told my flatmate i totally could do that if i was that height (Im 5'7) and he said no way because my vertical height in jumps weren't as high as these guys.

I'm not remotely athletic however i thought it would be interesting to look at the relationship between height and vertical jumps as these larger athletes don't need to jump as high a percentage of their overall height to dunk.

In this doc im going to pull some height and vertical jumping stats as well as compare them to the height of a standard nba ring to determine the % of their overall height to deliver a dunk.

## Height data

Lets pull some basic height data to work from. Justinas Cirtautas did a write up on kaggle last year on a similar topic,  You can read his analysis in the notebook here:
<https://www.kaggle.com/justinas/nba-height-and-weight-analysis/notebook> 

He's done a lot of heavy lifting here re: data scraping So lets thank him and  pull the base dataset from there.
I was going to pull this data using the kaggle API but ran into issues with authenticating the API without putting my credentials into this script. Therefore I have excluded that part and used the static data from:

https://www.kaggle.com/justinas/nba-height-and-weight-analysis/data?select=all_seasons.csv

extracted as at 2022/01/07 (YYY/MM/DD)

```{r, warning=FALSE}
#Load libraries and Cirtuata's csv
library(knitr)
library(ggplot2)

Kaggle_data <- read.csv("all_seasons.csv", stringsAsFactors = FALSE)

```


So lets have a quick look at what we've got

```{r}
head(Kaggle_data)

summary(Kaggle_data)

```

Im also interested in how the distribution of this data changes over time, Likewise, does this mean that our model should include some kinda of lag of exclusion of timeseries.

```{r}
gg_height_density <- ggplot(Kaggle_data, aes(x=player_height))+
  geom_density()+
  ggtitle("NBA Player Height in cm")+
  facet_wrap(~draft_year)

gg_height_density
```

